InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-14 paper.tex

>>>>

The \textbf{Falcon-RW-1B} model built by TII (\url{https://www.tii.ae/}) is the second text generative model we use to test our augmentation models. It is a decoder-only model trained on 350 billion tokens of the RefinedWeb data set. This data set leverages strict filtering and stringent deduplication to uplift the quality of web data. \cite{penedo2023refinedweb}
